%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Appointments}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Postdoctoral Associate, Schmitz Lab} % Job title
    {School of the Environment, Yale University} % Organization
    {New Haven, USA} % Location
    {Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Mathematical modeling work to animate ecosystem carbon budget and cycling models by accounting for animal effects and influences.}
      \end{cvitems} 
    }

%---------------------------------------------------------
  \cventry
    {Visiting Assistant in Research, Schmitz Lab} % Job title
    {School of the Environment, Yale University} % Organization
    {New Haven, USA} % Location
    {Feb. 2019--Apr. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Meta-ecosystem modeling work to describe the effects of animal-mediated nutrient transport across ecosystem boundaries.}
      \end{cvitems}  
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant, Pawar Lab} % Job title
    {Department of Life Sciences, Imperial College London} % Organization
    {Silwood Park, Ascot, UK} % Location
    {Jan. 2016--Mar. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Data collection, management, and cleanup for a meta-analysis of published studies of plant thermal responses.}
      \end{cvitems}  
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant, Tsaobis Baboon Project} % Job title
    {Zoological Society of London} % Organization
    {London, UK} % Location
    {Jun. 2015--Oct. 2015} % Date(s)
    {
       \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Field placement to collect behavioral and population data from wild, habituated \textit{Chacma} baboons, and conduct plant phenology survey.}
      \end{cvitems}  
    }

%---------------------------------------------------------
  \cventry
    {Research Assistant, Roe \& Red Deer in Trentino and Technology Project} % Job title
    {Fondazione Edmund Mach} % Organization
    {Trento, Italy} % Location
    {Jun. 2013--Sept. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Field placement to collect roe deer radio-tracking data, as well as conduct plant phenology surveys and pellet decay rate analyses.}
      \end{cvitems}   
    }

%---------------------------------------------------------
  \cventry
    {Graduate Intern, Piedmont Wolf Project} % Job title
    {Maritime Alps Nature Park} % Organization
    {Entracque (CN), Italy} % Location
    {Jun. 2011--Dec. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and led a mixed laboratory and field-based study of wolves-chamois predator-prey interactions in the Western Alps.}
      \end{cvitems} 
    }

%---------------------------------------------------------
  \cventry
    {Undergraduate Intern} % Job title
    {Ethology Lab, University of Turin} % Organization
    {Turin, Italy} % Location
    {Jul. 2008 - Mar. 2009} % Date(s)
    {
       \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Bio-acoustic study of the \textit{Indri} lemur to isolate individual contributions to a family group song.}
      \end{cvitems} 
    }

%---------------------------------------------------------
\end{cventries}
