%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentations}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\skilltypestyle{Conference Talks}

\begin{itemize}
  \setlength\itemsep{.25em}
  \item \textcolor{awesome}{Rizzuto, M.}, Leroux, S.J., Schmitz, O.J. (2024, Aug. 6--11) \emph{Modeling the zoogeochemical effects of herbivores on ecosystem carbon cycles.} ``For All Ecologists'' Ecological Society of America Annual Meeting, Portland, OR, USA. \textbf{\emph{Invited talk}}  
  \item \textcolor{awesome}{Rizzuto, M.}, Leroux, S.J., Schmitz, O.J. (2023, May 25) \emph{Modeling the zoogeochemical effects of herbivores on ecosystem carbon cycles.} 6\textsuperscript{th} Yale Postdoc Association Annual Symposium, New Haven, CT, USA.
  \item \textcolor{awesome}{Rizzuto, M.}, Leroux, S.J., Schmitz, O.J., Vander Wal, E., Wiersma, Y.F., Heckford, T.R. (2023, May 2--6 ) \emph{Movers and shakers: Animal-vectored nutrient flows across resource gradients influence local and meta-ecosystem functioning.} ``Ecological Models for Tomorrow's Solutions'' The International Society for Ecological Modelling Global Conference 2023, Toronto, ON, Canada.
  \item \textcolor{awesome}{Rizzuto, M.}, Leroux, S.J., Schmitz, O.J., Vander Wal, E., Wiersma, Y.F., Heckford, T.R. (2021, Aug. 2--6) \emph{Going against the flow: non-diffusive organismal movement influences local and meta-ecosystem functioning.} ``Vital Connections in Ecology'' Ecological Society of America Virtual Annual Meeting, Long Beach, CA, USA.
  \item \textcolor{awesome}{Rizzuto, M.}, Leroux, S.J., Vander Wal, E., Wiersma, Y.F., Heckford, T.R., Balluffi-Fry, J. (2018, Jul. 18--21) \emph{Ontogeny and Ecological Stoichiometry of Snowshoe hares (Lepus americanus) in the Boreal Forests of Newfoundland.} Canadian Society for Ecology and Evolution Annual General Meeting, Guelph, ON, Canada.
  \item \textcolor{awesome}{Rizzuto, M.}, Carbone, C., and Pawar, S. (2016, Jul. 7--11) \emph{Bio-mechanical constraints on foraging reverse the scaling of activity rate among carnivores.} Canadian Society for Ecology and Evolution Annual General Meeting, St. John's, NL, Canada.
\end{itemize}

\skilltypestyle{Conference Posters}

\begin{itemize}
  \item \textcolor{awesome}{Rizzuto, M.}, Leroux, S.J., Vander Wal, E., Wiersma, Y.F., Heckford, T.R., Balluffi-Fry, J. (2018, Jul. 21--27) \emph{Beyond Diffusion: Animal-Mediated Nutrient Transport at Different Spatial Scales.} ``Unifying Ecology Across Scales'' Gordon Research Seminar and Conference, Biddeford, ME, USA.
\end{itemize}

\skilltypestyle{Workshops}

\begin{itemize}
  \item \textcolor{awesome}{Rizzuto, M.} (4 Nov. 2022) \emph{Grammar of Graphics: ggplot2.} Part of SPRY: A Learning Community for Quantitative Skill-Sharing\\ Yale University, School of the Environment.
  \item \textcolor{awesome}{Rizzuto, M.} (14 Oct. 2022) \emph{(R)markdown: a brief tour.} Part of SPRY: A Learning Community for Quantitative Skill-Sharing\\ Yale University, School of the Environment.
\end{itemize}

\skilltypestyle{Outreach}

\begin{itemize}
  \item \textcolor{awesome}{Rizzuto, M.} (24 Sept. 2024) \emph{Understanding the evidence. The latest science on trophic rewilding.} ``Are wild animals the unsung heroes of climate action?'' Panel, International Fund for Animal Welfare, New York Climate Week.
\end{itemize}
\begin{itemize}
  \item \textcolor{awesome}{Rizzuto, M.} (26 Apr. 2024) \emph{How animals shape our world: ecosystems, nutrient cycling, and carbon capture.} Wolfram Ecological Research Colloquium.
\end{itemize}

\skilltypestyle{Skype-a-Scientist initiative}

\begin{itemize}
  \item Louisville Zoo, Louisville, KY, USA. (30 Apr. 2025) 
  \item Tri-West Middle School, Lizton, IN, USA. (4 Dec. 2024)
  \item Edward Jones Scientist Expo Week. (16 Apr. 2024)
  \item Hope Township Elementary School, Hope, NJ, USA. (22 Mar. 2023)
\end{itemize}

