%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{etaremune}
  \renewcommand\labelenumi{\bfseries\theenumi .}
  \item Heckford, T.R., Leroux, S.J., Vander Wal, E., \textcolor{awesome}{Rizzuto, M.}, Balluffi-Fry, J., Richmond, I.C., Wiersma, Y.F. 2022. \href{https://doi.org/10.1002/ece3.9244}{Ecoregion and community structure influences on the foliar elemental niche of balsam fir (\textit{Abies balsamea} (L.) Mill.) and white birch (\textit{Betula papyrifera} Marshall)}. \emph{Ecology and Evolution} \textbf{12}, e9244. 
  \item Little, C.J.\textsuperscript{\textdagger}, \textcolor{awesome}{Rizzuto, M.}\textsuperscript{\textdagger}, Luhring, T.M., Monk, J.D., Nowicki, R.J., Paseka, R.E., Stegen, J.C., Symons, C.C., Taub, F.B., Yan, J.D.L. 2022. \href{https://doi.org/10.1111/oik.08892}{Movement with Meaning: Integrating Information into Meta-Ecology}. \emph{Oikos} \textbf{8}, e08892. \null\hfill\textbf{\textit{Editor's~Choice}}
  \item Balluffi-Fry, J., Leroux, S.J., Wiersma, Y.F., Richmond, I.C., Heckford, T.R., \textcolor{awesome}{Rizzuto, M.}, Kennah, J.L., Vander Wal, E. 2022. \href{https://rdcu.be/cAY5a}{Integrating plant stoichiometry and feeding experiments: state-dependent forage choice and its implications on body mass.} \emph{Oecologia} \textbf{198}(3), 579--591.
  \item Richmond, I.C., Balluffi-Fry, J., Vander Wal, E., Leroux, S.J., \textcolor{awesome}{Rizzuto, M.}, Heckford, T.R., Kennah, J.L., Riefesel, G.R., Wiersma, Y.F. 2022. \href{https://academic.oup.com/jmammal/advance-article/doi/10.1093/jmammal/gyab130/6441781?guestAccessKey=8f89e422-7fb9-4ce9-a9dc-ccf46f3dd0cc}{Individual snowshoe hares manage risk differently: integrating stoichiometric distribution models and foraging ecology}. \emph{Journal of Mammalogy} \textbf{103}(1), 196--208.
  \item Heckford, T.R., Leroux, S.J., Vander Wal, E., \textcolor{awesome}{Rizzuto, M.}, Balluffi-Fry, J., Richmond, I.C., Wiersma, Y.F. 2022. \href{https://doi.org/10.1007/s10980-021-01334-3}{Spatially explicit correlates of plant functional traits inform landscape patterns of resource quality}. \emph{Landscape Ecology} \textbf{37}, 59--80.
  \item \textcolor{awesome}{Rizzuto, M.}, Leroux, S.J., Vander Wal, E., Richmond, I.C., Heckford, T.R., Balluffi-Fry, J., Wiersma, Y.F. 2021. \href{https://rdcu.be/cSX31}{Forage stoichiometry predicts the home range size of a small terrestrial herbivore}. \emph{Oecologia} \textbf{197}(2), 327--338. \hfill\textbf{\textit{Winner,~Hanski~Prize~2021}}
  \item Ellis-Soto, D.\textsuperscript{\textdagger}, Ferraro, K.M.\textsuperscript{\textdagger}, \textcolor{awesome}{Rizzuto, M.}, Briggs, E., Monk, J.D., and Schmitz, O.J. 2021. \href{https://doi.org/10.1111/1365-2656.13538}{A methodological roadmap to quantify animal-vectored spatial ecosystem subsidies}. \emph{Journal of Animal Ecology} \textbf{90}(7), 1605--1622. \hfill\textbf{\textit{Winner,~Sidnie~Manton~Award~2021}}
  \item Richmond, I.C., Leroux, S.J., Vander Wal, E., Heckford, T.R., \textcolor{awesome}{Rizzuto, M.}, Balluffi-Fry, J., Kennah, J., Wiersma, Y.F. 2021. \href{https://doi.org/10.1093/jpe/rtaa103}{Temporal variation and its drivers in the elemental traits of four boreal plant species}. \emph{Journal of Plant Ecology} \textbf{14}(3), 398--413.
  \item Balluffi-Fry, J., Leroux, S.J., Wiersma, Y.F., Heckford, T.R., \textcolor{awesome}{Rizzuto, M.}, Richmond, I.C., Vander Wal, E. 2020. \href{https://doi.org/10.1002/ece3.6975}{Quantity-quality trade-offs revealed using a multiscale test of herbivore resource selection on elemental landscapes}. \emph{Ecology and Evolution} \textbf{10}(24), 13847--13859.
  \item \textcolor{awesome}{Rizzuto, M.}, Leroux, S.J., Vander Wal, E., Wiersma, Y.F., Heckford, T.R., Balluffi-Fry, J. 2019. \href{https://doi.org/10.1002/ece3.5880}{Patterns and potential drivers of intraspecific variability in the body C, N, and P composition of a terrestrial vertebrate, the snowshoe hare (\textit{Lepus americanus})}. \textit{Ecology and Evolution} \textbf{9}(24), 14453--14464.
  \item \textcolor{awesome}{Rizzuto, M.}, Carbone, C., and Pawar, S. 2018. \href{https://doi.org/10.1038/s41559-017-0386-1}{Foraging constraints reverse the scaling of activity time in carnivores}. \emph{Nature Ecology and Evolution} \textbf{2}(2), 247--253. \null\hfill\textbf{\textit{Cover~Story}}
\end{etaremune}
